Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-04-25 paper.tex
Added info for RFNU in ALS phase

We investigated the following sampling techniques for the training set. 
In each method, we included the first row of the matrix (first 
generated file of each subject) and a random column (all files of a 
random subject) to avoid cold start issues. \todo{Check why the first line is not in random unreal}

@@

>>>>

We investigated the following sampling techniques for the training set. 
In each method, we included the first row of the matrix (first 
generated file of each subject) and a random column (all files of a 
random subject) to avoid cold start issues.

@@

The graphs show a continuous rise in the accuracy trend in all condition pairs however a 0.03 drop is recorder in C6C7 beteen training ratio size of $0.8$ to $0.9$. This metod takes over the dummy accuracy after having a training size over 40 percent in C5vsC7 and C6vsC7 but it always shows better acuracy than dummy classifier ($0.73$ percent with traininfg ratio of $0.1$)    
